---
title: "Data Science Project Management - Assignment IV"
author:
- "Leonard Berger" 
- "Student-ID: 5629475"
date: "16.02.2021"
output: html_document
---

  
  ```{r R-Markdown_setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE)
knitr::opts_knit$set(root.dir = "C:/Users/leona/OneDrive/Uni Tübingen Data Science/1. Semester/Data Science Project Management/Assignment 4")
```





### Preparation
Before beginning with the exercises, the workspace is cleared and packages are loaded. Then, the data path is specified.

```{r Preparation}

## Clearing workspace
rm(list=ls())

# set working directory
setwd("C:/Users/leona/OneDrive/Data Science Project Management/DSPM_Assignment_V")


## Installing packages
# install.packages("jsonlite")
# install.packages("httr")
# install.packages("rlist")
# install.packages("ggplot2")
# install.packages("dplyr")

library(jsonlite)
library(httr)
library(rlist)
library(ggplot2)
library(dplyr)



```



### Exercise 1 - Setting up a new GitHub repository

I set up a GitHub repository to store and track this project under "https://github.com/Lnrdbrgr/DSPM_Assignment_V". To work with Git I use the GUI provided by RStudio.


### Exercise 2 - Getting to know the API

I include the API from a different script. The Documentation states that 5000 API calls per day and 5 requests per second are allowed.

```{r Ex_2_API}
# include API Key
source("C:/Users/leona/OneDrive/Uni Tübingen Data Science/1. Semester/Data Science Project Management/Assignment 5/API_key.R")

```




### Exercise 3 - Interacting with the API

> Expand the model from exercise 2 by adding `log.uranium` as a county-level predictor.

To reproduce the results of Gelman, the basement variable is recoded.
```{r Ex_3_API_basics}
# contruct the API url with the API key searching for venues
api_url <- ("https://app.ticketmaster.com/discovery/v2/venues.json?")

# GET request
APIcontent <- GET(url = api_url,
                  query = list(apikey = API_key,
                               locale="*",
                               countryCode = "DE"))

# store the content
venue_results_ex3 <- content(APIcontent)
```

The resulting List has three elements. The locations seem to be stored in _embedded/venues. There, the locations are listed with Name, Address, country, etc... The latitude and longitude is storred in location. The List element pages tells us that each page has 20 results listed, the total number of results is 12236 contained on 612 pages.



```{r Ex_3_exp_model}
### Extracting name, city, postalCode, address, url, lat and long

# create empty data frame
venue_data <- data.frame("name" = rep(NA, 20),
                         "city" = rep(NA, 20),
                         "postalCode" = rep(NA, 20),
                         "address" = rep(NA, 20),
                         "url" = rep(NA, 20),
                         "longitude" = rep(NA, 20),
                         "latitude" = rep(NA, 20))


# how many results?
no_results <- venue_results_ex3$page$size


# extract the data from the list
for (i in 1:no_results){
  
  venue_data$name[i] <- venue_results_ex3$`_embedded`[[1]][[i]]$name
  venue_data$city[i] <- venue_results_ex3$`_embedded`[[1]][[i]]$city
  venue_data$postalCode[i] <- venue_results_ex3$`_embedded`[[1]][[i]]$postalCode
  venue_data$address[i] <- venue_results_ex3$`_embedded`[[1]][[i]]$address
  venue_data$url[i] <- venue_results_ex3$`_embedded`[[1]][[i]]$url
  
  # account for missing values in latitude and longitude
  if (!is.null(venue_results_ex3$`_embedded`[[1]][[i]]$location$longitude)){
    venue_data$longitude[i] <- venue_results_ex3$`_embedded`[[1]][[i]]$location$longitude
  }
  
  if (!is.null(venue_results_ex3$`_embedded`[[1]][[i]]$location$latitude)){
    venue_data$latitude[i] <- venue_results_ex3$`_embedded`[[1]][[i]]$location$latitude
  }
  
}


# perform some modification on the data types
venue_data$city <- as.character(venue_data$city)
venue_data$address <- as.character(venue_data$address)
venue_data$longitude <- as.numeric(venue_data$longitude)
venue_data$latitude <- as.numeric(venue_data$latitude)

# take a look on the data
glimpse(venue_data)
```




### Exercise 4 - Interacting with the API - advanced


```{r Ex_4_API_advanced}

# data frame to store results
venue_data <- data.frame("name" = NA,
                         "city" = NA,
                         "postalCode" = NA,
                         "address" = NA,
                         "url" = NA,
                         "longitude" = NA,
                         "latitude" = NA)





# get no. of pages we need to loop through
no_pages <- venue_results_ex3$page$totalPages

# contruct the API url with the API key searching for venues
api_url <- ("https://app.ticketmaster.com/discovery/v2/venues.json?")


for (i in 0:no_pages-3){
  
  # GET request
  APIcontent <- GET(url = api_url,
                    query = list(apikey = API_key,
                                 countryCode = "DE",
                                 locale="*",
                                 page = i))
  
  # get content
  venue_results <- content(APIcontent)
  
  # help data frame to store results
  venue_help_df <- data.frame("name" = rep(NA, 20),
                              "city" = rep(NA, 20),
                              "postalCode" = rep(NA, 20),
                              "address" = rep(NA, 20),
                              "url" = rep(NA, 20),
                              "longitude" = rep(NA, 20),
                              "latitude" = rep(NA, 20))
  
  
  # extract the data from the list
  for (j in 1:20){
    
    
    # account for missing values in latitude and longitude
    if (!is.null(venue_results$`_embedded`[[1]][[j]]$name)){
      venue_help_df$name[j] <- venue_results$`_embedded`[[1]][[j]]$name
    }
    
    if (!is.null(venue_results$`_embedded`[[1]][[j]]$city)){
      venue_help_df$city[j] <- venue_results$`_embedded`[[1]][[j]]$city
    }
    
    if (!is.null(venue_results$`_embedded`[[1]][[j]]$postalCode)){
      venue_help_df$postalCode[j] <- venue_results$`_embedded`[[1]][[j]]$postalCode
    }
    
    
    if(length(venue_results$`_embedded`[[1]][[j]]$address)==0){
      venue_help_df$address[j] <- NA
    } else if (!is.null(venue_results$`_embedded`[[1]][[j]]$address)){
      venue_help_df$address[j] <- venue_results$`_embedded`[[1]][[j]]$address
    }
    
    
    if (!is.null(venue_results$`_embedded`[[1]][[j]]$url)){
      venue_help_df$url[j] <- venue_results$`_embedded`[[1]][[j]]$url
    }
    
    
    if (!is.null(venue_results$`_embedded`[[1]][[j]]$location$longitude)){
      venue_help_df$longitude[j] <- venue_results$`_embedded`[[1]][[j]]$location$longitude
    }
    
    if (!is.null(venue_results$`_embedded`[[1]][[j]]$location$latitude)){
      venue_help_df$latitude[j] <- venue_results$`_embedded`[[1]][[j]]$location$latitude
    }
    
  }
  
  # perform some modification on the data types
  venue_help_df$city <- as.character(venue_help_df$city)
  venue_help_df$address <- as.character(venue_help_df$address)
  venue_help_df$longitude <- as.numeric(venue_help_df$longitude)
  venue_help_df$latitude <- as.numeric(venue_help_df$latitude)
  
  
  # ignore efficiency for the time being and append the data frame
  venue_data <- rbind(venue_data, venue_help_df)
  
  
  # sleep for X seconds to stay in line with the guidelines
  Sys.sleep(0.25)
  
}


# make some modifications to the data frame
venue_data_2 <- venue_data[-(1:61),]

glimpse(venue_data_2)


```









### Exercise 5 - Visualizing the extracted data


```{r Ex_5_Viz}
# adjust lat and long to extreme points of Germany
venue_data_2$longitude_mod <- ifelse((venue_data_2$longitude < 5.866944 | venue_data_2$longitude > 15.043611), NA, venue_data_2$longitude)
venue_data_2$latitude_mod <- ifelse((venue_data_2$latitude < 47.271679 | venue_data_2$latitude > 55.0846), NA, venue_data_2$latitude)


## set up a map of germany which diplays the locations of the venues
ggplot() +
  geom_polygon(
    aes(x = long, y = lat, group = group), data = map_data("world", region = "Germany"),
    fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across Germany", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic")) +
  geom_point(aes(x = longitude_mod,
                 y = latitude_mod),
             data = venue_data_2,
             alpha = 05,
             size = 0.7,
             col = "red")

```





### Exercise 6 - Event locations in other countries

Country of choice: Spain


```{r Ex_6_Spain}

# Perform the GET request examplary for the first page
APIcontent <- GET(url = api_url,
                  query = list(apikey = API_key,
                               locale = "*",
                               countryCode = "ES"))


APIcontent_Spain <- GET(url = api_url,
                        query = list(apikey = API_key,
                                     locale = "*",
                                     countryCode = "ES"))


venue_results_Spain <- content(APIcontent_Spain)


# extract the total number of Pages
no_pages_Spain <- venue_results_Spain$page$totalPages



### Extract all locations

## set up Data frame
venue_data_Spain <- data.frame("name" = NA,
                               "city" = NA,
                               "postalCode" = NA,
                               "address" = NA,
                               "url" = NA,
                               "longitude" = NA,
                               "latitude" = NA)


## loop through all pages and extract locations

for (i in 0:no_pages_Spain-2){
  
  # GET request
  APIcontent_Spain <- GET(url = api_url,
                          query = list(apikey = API_key,
                                       countryCode = "ES",
                                       locale="*",
                                        page = i))
  
  # get content
  venue_results_Spain <- content(APIcontent_Spain)
  
  # help data frame to store results
  venue_help_df_Spain <- data.frame("name" = rep(NA, 20),
                                    "city" = rep(NA, 20),
                                    "postalCode" = rep(NA, 20),
                                    "address" = rep(NA, 20),
                                    "url" = rep(NA, 20),
                                    "longitude" = rep(NA, 20),
                                    "latitude" = rep(NA, 20)) 
  
  
  # extract the data from the list
  for (j in 1:20){
    
    
    # account for missing values in latitude and longitude
    if (!is.null(venue_results_Spain$`_embedded`[[1]][[j]]$name)){
      venue_help_df_Spain$name[j] <- venue_results_Spain$`_embedded`[[1]][[j]]$name
    }
    
    if (!is.null(venue_results_Spain$`_embedded`[[1]][[j]]$city)){
      venue_help_df_Spain$city[j] <- venue_results_Spain$`_embedded`[[1]][[j]]$city
    }
    
    if (!is.null(venue_results_Spain$`_embedded`[[1]][[j]]$postalCode)){
      venue_help_df_Spain$postalCode[j] <- venue_results_Spain$`_embedded`[[1]][[j]]$postalCode
    }
    
    
    if(length(venue_results_Spain$`_embedded`[[1]][[j]]$address)==0){
      venue_help_df_Spain$address[j] <- NA
    } else if (!is.null(venue_results_Spain$`_embedded`[[1]][[j]]$address)){
      venue_help_df_Spain$address[j] <- venue_results_Spain$`_embedded`[[1]][[j]]$address
    }
    
    
    if (!is.null(venue_results_Spain$`_embedded`[[1]][[j]]$url)){
      venue_help_df_Spain$url[j] <- venue_results_Spain$`_embedded`[[1]][[j]]$url
    }
    
    
    if (!is.null(venue_results_Spain$`_embedded`[[1]][[j]]$location$longitude)){
      venue_help_df_Spain$longitude[j] <- venue_results_Spain$`_embedded`[[1]][[j]]$location$longitude
    }
    
    if (!is.null(venue_results_Spain$`_embedded`[[1]][[j]]$location$latitude)){
      venue_help_df_Spain$latitude[j] <- venue_results_Spain$`_embedded`[[1]][[j]]$location$latitude
    }
    
  }
  
  # perform some modification on the data types
  venue_help_df_Spain$city <- as.character(venue_help_df_Spain$city)
  venue_help_df_Spain$address <- as.character(venue_help_df_Spain$address)
  venue_help_df_Spain$longitude <- as.numeric(venue_help_df_Spain$longitude)
  venue_help_df_Spain$latitude <- as.numeric(venue_help_df_Spain$latitude)
  
  
  # ignore efficiency for the time being and append the data frame
  venue_data_Spain <- rbind(venue_data_Spain, venue_help_df_Spain)
  
  
  # sleep for X seconds to stay in line with the guidelines
  Sys.sleep(0.25)
  
}



## make some modifications to the resulting data frame
venue_data_Spain_2 <- venue_data_Spain[-(1:41),] 

glimpse(venue_data_Spain_2)
```


```{r Ex_6_Spain_Viz}
# adjust lat and long to extreme points of Spain
venue_data_Spain_2$longitude_mod <- ifelse((venue_data_Spain_2$longitude < -9.3 | venue_data_Spain_2$longitude > 3.316667), NA, venue_data_Spain_2$longitude)
venue_data_Spain_2$latitude_mod <- ifelse((venue_data_Spain_2$latitude < 36 | venue_data_Spain_2$latitude > 43.783333), NA, venue_data_Spain_2$latitude)



## set up a map of Spain which diplays the locations of the venue
## here I concentrate on the mainland
ggplot() +
  geom_polygon(
    aes(x = long, y = lat, group = group), data = map_data("world", region = "Spain"),
    fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across Spain", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic")) +
  geom_point(aes(x = longitude_mod,
                 y = latitude_mod),
             data = venue_data_Spain_2,
             alpha = 0.5,
             size = 0.7,
             col = "red")





```









